Analysis of Odd one out experiment

### 2019-06-27 reports/odd_one_out/analysis_oddoneout.Rmd
change some translations

p <- df_onecat_distances %>% 
  ggplot(aes(x = distance)) + 
  geom_histogram(bins = 30) + 
  theme(aspect.ratio = 1) +
  geom_segment(data = df_segments, aes(x=x,xend=xend,y=y,yend=yend)) +
  annotate(x = qs[3:5]-c(3,1,-0.6), y = c(19,19,19), label = c("2.","3.","4."), geom = "label", size = 5) +
  ggtitle(sprintf("Kategorie: %s",this_cat)) +
  xlab("Vzdálenost") +
  ylab("Počet")
p  
ggsave(file.path(plots_dir, "Fig_distance_histogram.eps"), p, width = 6, height = 6)  
```

@@

  #scale_x_continuous("Kvintil", breaks = c(2,3,4), labels = c("2","3","4")) + 
  geom_violin(trim = F)+
  stat_summary(fun.data = "mean_cl_boot") + 
  xlab("Kvintil") + 
  ylab("Správnost")

@@

p_ordercat <- order_category %>%
  ggplot(aes(x = category, xend = category, y = Lower, yend = Upper, group = 1, col = category_type)) +
  geom_segment(size = 1.2) +
  geom_point(aes(y=Mean), size = 3) + 
  theme(aspect.ratio = 0.2) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 16)) + 
  theme(legend.position = "top") + 
  xlab("Category") + 
  ylab("Accuracy") + 
  scale_color_discrete("Category type", labels = c("Man-made","Natural")) 
p_ordercat
ggsave(file.path(plots_dir, "Fig_chp3_ordercat.eps"), p_ordercat, width = 18, height = 6)
```

@@

```{r}
dredge.models<-dredge(glm2,trace=FALSE,rank="AICc")
my.dredge.models<-get.models(dredge.models,subset = T)
silly<-model.avg(my.dredge.models,subset=delta<10)
predict(silly,type="response")

@@

predframe$correct <- predict(glm2,newdata=predframe,type="response",re.form=NA)
p <- p0 + geom_point(data=predframe,colour="red")+
  geom_line(data=predframe,colour="red",aes(group=1)) + 
  ylim(0,1)+
  theme(aspect.ratio = 1) +
  geom_hline(yintercept = 1/9) +
  xlab("Poměr vzdáleností") + 
  ylab("Správnost")

p
ggsave(file.path(plots_dir, "Fig_chp3_results_ratio.eps"), p, width = 6, height = 6)

@@

p1 <- onecat_plot(bottom_one$category[1])
p2 <- onecat_plot(top_one$category[1])
ggsave(file.path(plots_dir, "Fig_chp3_category_closet.eps"), p1, width = 6, height = 6)
ggsave(file.path(plots_dir, "Fig_chp3_category_field.eps"), p2, width = 6, height = 6)
```

>>>>

p <- df_onecat_distances %>% 
  ggplot(aes(x = distance)) + 
  geom_histogram(bins = 30) + 
  theme(aspect.ratio = 1) +
  geom_segment(data = df_segments, aes(x=x,xend=xend,y=y,yend=yend)) +
  annotate(x = qs[3:5]-c(3,1,-0.6), y = c(19,19,19), label = c("2.","3.","4."), geom = "label", size = 5) +
  ggtitle(sprintf("Category: %s",this_cat)) +
  xlab("Distance") +
  ylab("Count")
p  
ggsave(file.path(plots_dir, "Fig_chp3_distance_histogram.svg"), p, width = 6, height = 6)  
```

@@

  #scale_x_continuous("Kvintil", breaks = c(2,3,4), labels = c("2","3","4")) + 
  geom_violin(trim = F)+
  stat_summary(fun.data = "mean_cl_boot") + 
  xlab("Quintile")

@@

p_ordercat <- order_category %>%
  ggplot(aes(x = category, xend = category, y = Lower, yend = Upper, group = 1, col = category_type)) +
  geom_segment(size = 1.2) +
  geom_point(aes(y=Mean), size = 3) + 
  theme(aspect.ratio = 0.2) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 16)) + 
  theme(legend.position = "top") + 
  xlab("Category") + 
  ylab("Perc. correct") + 
  scale_color_discrete("Category type", labels = c("Man-made","Natural")) 
p_ordercat
ggsave(file.path(plots_dir, "Fig_chp3_ordercat.svg"), p_ordercat, width = 18, height = 6)
```

@@

```{r}
#dredge.models<-dredge(glm2,trace=FALSE,rank="AICc")
#my.dredge.models<-get.models(dredge.models,subset = T)
#silly<-model.avg(my.dredge.models,subset=delta<10)
#predict(silly,type="response")

@@

predframe$correct <- predict(glm2,newdata=predframe,type="response",re.form=NA)
p <- p0 + geom_point(data=predframe,colour="red")+
  geom_line(data=predframe,colour="red",aes(group=1)) + 
  ylim(0,1)+
  theme(aspect.ratio = 1) +
  geom_hline(yintercept = 1/9) +
  xlab("Distance ratio") + 
  ylab("Perc. correct")

p
ggsave(file.path(plots_dir, "Fig_chp3_results_ratio.svg"), p, width = 6, height = 6)

@@

p1 <- onecat_plot(bottom_one$category[1])
p2 <- onecat_plot(top_one$category[1])
ggsave(file.path(plots_dir, "Fig_chp3_category_closet.svg"), p1, width = 6, height = 6)
ggsave(file.path(plots_dir, "Fig_chp3_category_field.svg"), p2, width = 6, height = 6)
```
